Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-17 ms.tex
showing behavior during TMC oscillations

>>>>

\subsubsection{FPA Temperature Oscillations}
When the temperature control loop on the FPA is working improperly, there can be oscillations in the FPA temperature, as shown in Figure \ref{fig:indTSeriesTMCoscillations}.
In this example, the oscillations happen at a period of 19.3 minutes.
The LED fluctuations are signfiicantly longer with a period of $\sim$100 to $\sim$125 minutes.

\begin{figure*}
{\gridline{\fig{individual_azlab06_sub320_tmc_oscillations.pdf}{0.99\textwidth}{}}}
\caption{Time series during a $\sim$ 20 minute oscillation in the TMC temperature.}\label{fig:indTSeriesTMCoscillations}
\end{figure*}
